paper_data

### 2024-03-18 paper_codes.Rmd
update

---
title: "Paper Codes"
author: "Markus Viljanen"
date: "2023-08-09"
output: html_document
---

@@

## Plot field visits

@@

```{r}
# Linear terms
terms.plot <- terms %>% filter((term == "fixed") & (ID != "intercept")) %>% 
  mutate(ID=fct_relevel(ID, "ORG_STOF.z", "CN.z", "N_totaal.z", "P_totaal.z", "K_CaCl2.z")) %>% #"intercept", 
  mutate(term=recode(term, "fixed" = "Abiotic (z-score)")) %>%
  mutate(meta=factor(recode(meta, "Certain" = "Two-Stage", "Uncertain"="Joint"), levels=c("Two-Stage", "Joint")))
plot.abiotic <- ggplot(terms.plot, aes(x=ID, y=mean, col=meta, group=meta)) + 
  geom_point(position=position_dodge(width=0.5), size=2) +
  geom_errorbar(position=position_dodge(width=0.5), aes(ymin=X0.025quant, ymax=X0.975quant)) +
  theme(legend.position="top", axis.text.x = element_text(angle = 90)) + 
  scale_color_discrete(name = "Model Abiotics") +
  scale_x_discrete(name='Covariate') + 
  scale_y_continuous(name='Value') + #coord_cartesian(ylim=c(-5,5))+ #ylim=c(-10,10)
  facet_wrap( ~ term, ncol = 10, scales="free")
plot.abiotic
```

@@

```{r}
# Spatial terms (abiotics)
terms.plot <- terms %>% filter((term =="spatial") & (model != "SDM")) %>%
  mutate(ID=fct_relevel(ID, "log.range", "log.variance", "log.variance.eps")) %>%
  mutate(term=recode(term, "spatial" = "Spatial (km)"))%>%
  mutate(meta=factor(recode(meta, "Certain" = "Two-Stage", "Uncertain"="Joint"), levels=c("Two-Stage", "Joint")))
plot.extrapolate <- ggplot(terms.plot, aes(x=ID, y=mean, col=meta, group=meta)) + 
  geom_point(position=position_dodge(width=0.5), size=2) +
  geom_errorbar(position=position_dodge(width=0.5), aes(ymin=X0.025quant, ymax=X0.975quant)) +
  theme(legend.position="top", axis.text.x = element_text(angle = 90)) + 
  scale_color_discrete(name = "Model Abiotics") +
  scale_x_discrete(name='Covariate') + 
  scale_y_continuous(name='Value') +
  facet_wrap( ~ model, ncol = 10, scales="free")
plot.extrapolate
```

@@

```{r}
# Leave province out
sf.grid$provincie <- as.factor(sf.grid$naam)
plot.validation.1 <- ggplot(sf.grid) +
	geom_sf(aes(geometry=geometry.1, fill=provincie)) + 
	geom_sf(fill=NA, data=NL) +
  scale_fill_discrete(name = "Province") +
	ggtitle('Leave-province-out')

# Leave FGR region out
sf.grid$fgr <- factor(sf.grid$lmf_indeling, levels=c("afz", "duo", "duw", "hll", "hzn", "hzo", "hzv",
                                                     "hzz", "lvh", "lvn", "riv", "zkm", "zkn", "zkz"))
plot.validation.2 <- ggplot(sf.grid) +
	geom_sf(aes(geometry=geometry.1, fill=fgr)) + 
	geom_sf(fill=NA, data=NL) +
  scale_fill_manual(name = "FGR", values=c("afz"="lightseagreen", "duo"="darkgoldenrod", "duw"="darkgoldenrod1", "hll"="forestgreen", 
                                           "hzn"="wheat1", "hzo"="wheat2", "hzv"="wheat3", "hzz"="wheat4", 
                                           "lvh"="darkseagreen", "lvn"="darkseagreen1", "riv"="steelblue", 
                                           "zkm"="snow2", "zkn"="snow3", "zkz"="snow4")) +
	ggtitle('Leave-FGR-out')

# Combine plots
plot.all <- ggdraw() +
  draw_plot(plot.validation.1, x = 0, y = 0, width = 0.53, height = 1) +
  draw_plot(plot.validation.2, x = 0.53, y = 0, width = 0.47, height = 1) +
  draw_plot_label(label = c("A", "B"), size = 15, x = c(0.01, 0.53), y = c(0.99,0.99)) +
  theme(plot.background = element_rect(fill = "white", colour = NA))
plot.all
ggsave('results_paper/leave_out_validation.png', width=2500, heigh=1300, units='px')

>>>>

---
title: "Paper Codes"
author: "Makrus Viljanen"
date: "2023-08-09"
output: html_document
---

@@

##Plot grid

```{r}
colors = c("#1f77b4","#64a9d9","#bfe4ff",
          "#ff7f0e","#ffae66","#ffddbf",
          "#2ca02c","#6acf6a","#bfffbf",
          "#d62627","#ea6d6e","#ffbfbf",
          "#9466bd","#b88fde","#e0bfff")
names(colors) = c('Closed estuaries',
 'Dunes mainland',
 'Dunes Wadden islands',
 'Higher sandy soils East',
 'Higher sandy soils North',
 'Higher sandy soils South',
 'Higher sandy soils Veluwe',
 'Hill country Limburg ',
 'Low peat Holland',
 'Low peat North',
 'River area ',
 'Sea clay middle',
 'Sea clay North',
 'Sea clay South ',
 'Tidal areas Zeeland')
ggplot(NL) + geom_sf() +
	geom_sf(aes(geometry=geometry.1, fill=lmf_english,linewidth=0.1,colour=""), data=sf.grid) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',name='Physical Geological Region') +
  scale_colour_manual(values=NA) +
  guides(colour=guide_legend("Not mappable", override.aes=list(colour="gray"))) +
  scale_y_continuous(breaks = c(-100,0, 100), labels = c("363000","463000", "563000")) +
  scale_x_continuous(breaks = c(-100,0, 100), labels = c("55000","155000", "255000")) +
	theme(legend.position="right") #+ggtitle('Grid of Netherlands: Landuse') 
ggsave('results_paper/fgr.png', width=1600, heigh=1500, units='px')
```

```{r}
prov_geom <- read_sf("provincies.gpkg")$geom
prov_geom <- (prov_geom - matrix(data=c(155000, 463000), ncol=2)) * matrix(data=c(1/1000, 1/1000), ncol=2)
colors = c("#1f77b4","#aec7e8",
          "#ff7f0e","#ffba78",
          "#2ca02c","#98df8a",
          "#d62627","#ff9896",
          "#9466bd","#c5b0d5",
          "#8c564b","#c49c94")
names(colors) = c('Drenthe',
 'Flevoland',
 'Fryslân',
 'Gelderland',
 'Groningen',
 'Limburg',
 'Noord-Brabant',
 'Noord-Holland',
 'Overijssel',
 'Utrecht',
 'Zeeland',
 'Zuid-Holland')
ggplot() + 
	geom_sf(aes(geometry=geometry.1, fill=naam,linewidth=0.1), data=sf.grid) +
  geom_sf(aes(geometry=prov_geom),fill=NA) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',name='Province') +
  scale_y_continuous(breaks = c(-100,0, 100), labels = c("363000","463000", "563000")) +
  scale_x_continuous(breaks = c(-100,0, 100), labels = c("55000","155000", "255000")) +
	theme(legend.position="right") #+ggtitle('Grid of Netherlands: Landuse') 
ggsave('results_paper/provinces.png', width=1600, heigh=1200, units='px')

```
## Plot field visits

@@

```{r}
# Linear terms
labels <- c("Organic Material","Carbon/Nitrogen","Nitrogen","Phosphor","Potassium")
terms.plot <- terms %>% filter((term == "fixed") & (ID != "intercept")) %>% 
  mutate(ID=fct_relevel(ID, "ORG_STOF.z", "CN.z", "N_totaal.z", "P_totaal.z", "K_CaCl2.z")) %>% #"intercept", 
  mutate(term=recode(term, "fixed" = "Abiotic (z-score)")) %>%
  mutate(meta=factor(recode(meta, "Certain" = "Two-Stage", "Uncertain"="Joint"), levels=c("Two-Stage", "Joint")))
plot.abiotic <- ggplot(terms.plot, aes(x=ID, y=mean, col=meta, group=meta)) + 
  geom_point(position=position_dodge(width=0.5), size=2) +
  geom_errorbar(position=position_dodge(width=0.5), aes(ymin=X0.025quant, ymax=X0.975quant)) +
  theme(legend.position="top", axis.text.x = element_text(angle = 90)) + 
  scale_color_discrete(name = "Model Abiotics") +
  scale_x_discrete(name='Covariate',labels= labels) + 
  scale_y_continuous(name='Value') + #coord_cartesian(ylim=c(-5,5))+ #ylim=c(-10,10)
  facet_wrap( ~ term, ncol = 10, scales="free")
plot.abiotic
```

@@

```{r}
# Spatial terms (abiotics)
terms.plot <- terms %>% filter((term =="spatial") & (model != "SDM")) %>%
  mutate(ID=fct_relevel(ID, "log.range", "log.variance", "log.variance.eps")) %>%
  mutate(term=recode(term, "spatial" = "Spatial (km)"))%>%
  mutate(meta=factor(recode(meta, "Certain" = "Two-Stage", "Uncertain"="Joint"), levels=c("Two-Stage", "Joint"))) %>%
  mutate(model=recode(model, "ORG_STOF.z"="Organic Material","CN.z"="Carbon/Nitrogen","N_totaal.z"="Nitrogen","P_totaal.z"="Phosphor","K_CaCl2.z"="Potassium"))
plot.extrapolate <- ggplot(terms.plot, aes(x=ID, y=mean, col=meta, group=meta)) + 
  geom_point(position=position_dodge(width=0.5), size=2) +
  geom_errorbar(position=position_dodge(width=0.5), aes(ymin=X0.025quant, ymax=X0.975quant)) +
  theme(legend.position="top", axis.text.x = element_text(angle = 90)) + 
  scale_color_discrete(name = "Model Abiotics") +
  scale_x_discrete(name='Covariate') + 
  scale_y_continuous(name='Value') +
  facet_wrap( ~ model, ncol = 10, scales="free")
plot.extrapolate
```

@@

```{r}
colors = c("#1f77b4","#64a9d9","#bfe4ff",
          "#ff7f0e","#ffae66","#ffddbf",
          "#2ca02c","#6acf6a","#bfffbf",
          "#d62627","#ea6d6e","#ffbfbf",
          "#9466bd","#b88fde","#e0bfff")
names(colors) = c('Closed estuaries',
 'Dunes mainland',
 'Dunes Wadden islands',
 'Higher sandy soils East',
 'Higher sandy soils North',
 'Higher sandy soils South',
 'Higher sandy soils Veluwe',
 'Hill country Limburg ',
 'Low peat Holland',
 'Low peat North',
 'River area ',
 'Sea clay middle',
 'Sea clay North',
 'Sea clay South ',
 'Tidal areas Zeeland')
plot.validation.2 <- ggplot(NL) + geom_sf() +
	geom_sf(aes(geometry=geometry.1, fill=lmf_english,linewidth=0.1,colour=""), data=sf.grid) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',name='Physical Geological Region') +
  scale_colour_manual(values=NA) +
  guides(colour=guide_legend("Not mappable", override.aes=list(colour="gray"))) +
  scale_y_continuous(breaks = c(-100,0, 100), labels = c("363000","463000", "563000")) +
  scale_x_continuous(breaks = c(-100,0, 100), labels = c("55000","155000", "255000")) +
	theme(legend.position="right") +ggtitle('Leave-FGR-out')

prov_geom <- read_sf("provincies.gpkg")$geom
prov_geom <- (prov_geom - matrix(data=c(155000, 463000), ncol=2)) * matrix(data=c(1/1000, 1/1000), ncol=2)
colors = c("#1f77b4","#aec7e8",
          "#ff7f0e","#ffba78",
          "#2ca02c","#98df8a",
          "#d62627","#ff9896",
          "#9466bd","#c5b0d5",
          "#8c564b","#c49c94")
names(colors) = c('Drenthe',
 'Flevoland',
 'Fryslân',
 'Gelderland',
 'Groningen',
 'Limburg',
 'Noord-Brabant',
 'Noord-Holland',
 'Overijssel',
 'Utrecht',
 'Zeeland',
 'Zuid-Holland')
plot.validation.1 <- ggplot() + 
	geom_sf(aes(geometry=geometry.1, fill=naam,linewidth=0.1), data=sf.grid) +
  geom_sf(aes(geometry=prov_geom),fill=NA) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',name='Province') +
  scale_y_continuous(breaks = c(-100,0, 100), labels = c("363000","463000", "563000")) +
  scale_x_continuous(breaks = c(-100,0, 100), labels = c("55000","155000", "255000")) +
	theme(legend.position="right") +ggtitle('Leave-province-out')

# Combine plots
plot.all <- ggdraw() +
  draw_plot(plot.validation.1, x = 0, y = 0, width = 0.50, height = 1) +
  draw_plot(plot.validation.2, x = 0.49, y = 0, width = 0.55, height = 1) +
  draw_plot_label(label = c("A", "B"), size = 15, x = c(0.01, 0.50), y = c(0.99,0.99)) +
  theme(plot.background = element_rect(fill = "white", colour = NA))
plot.all
ggsave('results_paper/leave_out_validation.png', width=4600, heigh=1800, units='px')

### 2024-03-18 paper_data.Rmd
update

---
title: "paper_data"
author: "Markus Viljanen"
date: "2023-08-09"
output: html_document
---

@@

```{r}
conn <- dbConnect(PostgreSQL(), dbname="geodata", user = "", password="", host = "geodatabase.rivm.nl")
NL <- st_read(conn, query = "SELECT * FROM nl.adm_wijkbuurt_2022_gen;") %>%
  filter(indeling == 'gemeente') %>% st_union()
st_write(NL, "data_paper/NL.shp", append=F)
```

@@

```{r}
# Grid with rectangles and their centers  #%>% st_as_sf(crs=st_crs(NL))
grid.rect <- st_make_grid(NL,n=100,crs=st_crs(NL), what='polygons', square=T) 
grid.circle <- st_make_grid(NL,n=100,crs=st_crs(NL), what='centers')
index <- which(lengths(st_within(grid.circle, NL)) > 0) #st_intersects(grid.rect, NL)
# Create data frame
sf.grid <- data.frame(grid.circle[index], grid.rect[index]) %>% st_as_sf(crs=st_crs(NL))
sf.grid[c("X", "Y")] <- sf.grid %>% st_geometry %>% st_centroid() %>% st_coordinates()
sf.grid$Plot <- factor(sprintf("Grid%d", 1:nrow(sf.grid)))
```

@@

sf.plots <- sf.plots %>% st_join(provincie , left=T, st_within)
sf.grid <- sf.grid %>% st_join(provincie , left=T, st_within)
#plot(provincie)
```

>>>>

---
title: "paper_data"
author: "Makrus Viljanen"
date: "2023-08-09"
output: html_document
---

@@

```{r}
conn <- dbConnect(PostgreSQL(), dbname="geodata", user = "ro", password="ro!geo", host = "geodatabase.rivm.nl")
NL <- st_read(conn, query = "SELECT * FROM nl.adm_wijkbuurt_2022_gen;") %>%
  filter(indeling == 'gemeente') %>% st_union()
st_write(NL, "data_paper/NL.shp", append=F)
```

@@

```{r}
# Grid with rectangles and their centers  #%>% st_as_sf(crs=st_crs(NL))
grid.rect <- st_make_grid(NL,n=100,crs=st_crs(NL), what='polygons', square=T) 
grid.circle <- st_make_grid(NL,n=100,crs=st_crs(NL), what='centers')
index <- which(lengths(st_within(grid.circle, NL)) > 0) #st_intersects(grid.rect, NL)
# Create data frame
sf.grid <- data.frame( grid.rect[index]) %>% st_as_sf(crs=st_crs(NL))
sf.grid[c("X", "Y")] <- sf.grid %>% st_geometry %>% st_centroid() %>% st_coordinates()
sf.grid$Plot <- factor(sprintf("Grid%d", 1:nrow(sf.grid)))
```

@@

sf.plots <- sf.plots %>% st_join(provincie , left=T, st_within)
sf.grid <- sf.grid %>% st_join(provincie , left=T, st_within)
# plot(provincie)
```
